\EVOSUITE at the SBST 2019 Tool Competition

### 2019-03-22 papers/sbst19/paper_sbst19.tex
Added commands for the other tools.
T3 results.
Draft problematic challenges.

\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
\newcommand{\JTEXPERT}{{\sc jTExpert}\xspace}
\newcommand{\RANDOOP}{{\sc Randoop}\xspace}
\newcommand{\TT}{{\sc T3}\xspace}

@@

@@

\TODO{why did we get 0\% coverage on most AUTHZFORCE benchmarks? and SPOON-169,
SPOON-25?}

\TODO{why did we get 0\% coverage on DUBBO-2 and WEBMAGIC-4? classpath was
incorrect.}

\TODO{what did we get 0\% coverage on SPOON-253, SPOON-20, SPOON-16, SPOON-155
for larger search budgets?}

\TODO{why did not we get data for FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42,
SPOON-105 for a search budget of 10 seconds?}

%~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
%WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
%(highlighted in grey in Table~\ref{table:results}). The former two
%benchmarks had missing dependencies in the competition
%setup~\cite{sbst18competition}, which explains why \EVOSUITE was
%incapable of generating any test: When a dependency of the class under
%test is missing, then \EVOSUITE intentionally aborts with an error to
%inform the user of the configuration error. While this is desirable
%behavior during regular usage, arguably in the scope of the
%competition \EVOSUITE could try to ignore such errors and try to
%generate tests nevertheless, as it might still be possible to cover
%code even with some missing dependencies.

%For the REDISSON benchmarks, most
%executions ended with a timeout; unfortunately, we have not been able
%to reproduce this behaviour locally, hence we can only conjecture that
%the timeouts (reported during the initialisation phase) are due to the
%large number of dependency classes (>7000) that need to be loaded for
%these benchmarks to start off the test generation.

>>>>

\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
\newcommand{\JTEXPERT}{{\sc jTExpert}\xspace}
\newcommand{\RANDOOP}{{\sc Randoop}\xspace}
\newcommand{\TT}{{\sc T3}\xspace}
\newcommand{\SUSHI}{{\sc Sushi}\xspace}
\newcommand{\TARDIS}{{\sc Tardis}\xspace}

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:t3_results}Detailed results of \TT on the
    SBST benchmark classes.}
\vspace{-1em}
\resizebox{\textwidth}{!}{  
\input{mainTable-t3.tex}
}	
\end{table*}

@@

\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2, SPOON-169,
SPOON-25, and WEBMAGIC-4, and generally struggled with most AUTHZFORCE
benchmarks (highlighted in grey in Table~\ref{table:results}).

The benchmarks DUBBO-2 and WEBMAGIC-4 had missing dependencies in the
competition setup~\cite{sbst19competition} (something we reported last
year~\cite{evosuiteAtSbst2018}), which explains why \EVOSUITE was incapable of
generating any test: When a dependency of the class under test is missing, then
\EVOSUITE intentionally aborts with an error to inform the user of the
configuration error. While this is desirable behavior during regular usage,
arguably in the scope of the competition \EVOSUITE could try to ignore such
errors and try to generate tests nevertheless, as it might still be possible to
cover code even with some missing dependencies. For the benchmark FASTJSON-3 and
a 10s time budget, \EVOSUITE generated some test suites but due to a bug in the
competition infrastructure, no data was collected. % FileNotFoundException in the infrastructure

For the benchmarks SPOON-169 and SPOON-25, \EVOSUITE either failed to generated
a compilable test suite or crashed due to a bug in DynaMOSA. Although \EVOSUITE's
minimization could help at reducing the number of uncompilable / flaky test cases,
for SPOON-169 all minimizations attempts ran out of time.
% SPOON-169
% Minimization timeout. Roll back to original test suite
% and therefore the test suite

For the AUTHZFORCE benchmarks, although \EVOSUITE managed to generate some test
suites, most executions ended with a failure, unfortunately, we have not been
able to reproduce this behaviour locally, hence we cannot conjecture the reason
of such failures. \TODO{exact the same happened for SPOON-253 (120s and 240s).
Some sort of java.lang.SecurityException: Security manager blocks ("java.lang.RuntimePermission" "setSecurityManager").}

For a 10 seconds time budget, Table~\ref{table:results} reports ``-'' for
benchmarks FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42, and SPOON-105.
% last message in the log files was * Initial Number of Goals in DynMOSA = 942 / 10337
\TODO{either infinite loop, took much time to start evolving, or DynaMOSA can't
be used in this benchmarks with a time budget of 10s.}
%
On the other hand, and surprisingly, for benchmarks SPOON-155, SPOON-16,
SPOON-20, and SPOON-211, \EVOSUITE successfully generated test suites for small
time budgets but it failed to do it for large time budgets. For all, \EVOSUITE
crashed due to a bug in the DynaMOSA algorithm.
%% SPOON-155 (240s), SPOON-16 (120s), SPOON-20 (120s and 240s), SPOON-211 (120s)
%java.lang.NullPointerException: null
%	at org.evosuite.ga.operators.ranking.RankBasedPreferenceSorting.getNumberOfSubfronts(RankBasedPreferenceSorting.java:158) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.ga.metaheuristics.mosa.DynaMOSA.generateSolution(DynaMOSA.java:152) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.strategy.MOSuiteStrategy.generateTests(MOSuiteStrategy.java:115) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
